---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-files/",
  fig.retina = 3,
  out.width = "100%"
)
```

- Pronouns: She/Her
- How to reach me: 
  - mastodon: [@DrMowinckels@fosstodon.org](https://fosstodon.org/web/@Drmowinckels)
  - website:  [DrMowinckels](https://drmowinckels.io/)

I'm part of the [R-Ladies](https://rladies.org/) global team, where I particularly focus on the website development and maintenance, as well as the YouTube channel. 
I am a Certified [Sorftware Carpentry](https://software-carpentry.org/) Instructor, where I am able to teach git, bash and R lessons, and a Certified [Posit Tidyverse instructor](https://education.rstudio.com/trainers/people/mowinckel+athanasia/).

I work as a staff scientist at [the Center for Lifespan Changes in Brain and Cognition](www.oslobrains.no) at the University of Oslo.

  
[![GitHub stats](https://github-readme-stats.vercel.app/api?username=drmowinckels&show_icons=true&theme=transparent)](https://github.com/anuraghazra/github-readme-stats)


## Skills
<table border="1px solid black" style="margin: 5px">
 <tr>
    <td><b style="font-size:30px">I have</b></td>
    <td><b style="font-size:30px">I'm learning</b></td>
    <td><b style="font-size:30px">In the memory banks</b></td>
 </tr>
 <tr>
    <td>
        <img src="https://skillicons.dev/icons?i=r,bash,git,sass,html,css,bootstrap,github,githubactions,md&perline=3" />
    </td>
    <td>
      <img src="https://skillicons.dev/icons?i=js,regex&perline=3" />
      <br>
      <img src="https://img.shields.io/badge/Airtable-18BFFF?style=for-the-badge&logo=Airtable&logoColor=white" /><br>
      <img src="https://img.shields.io/badge/Airflow-017CEE?style=for-the-badge&logo=Apache%20Airflow&logoColor=white" /><br>
      <img src="https://img.shields.io/badge/Jenkins-D24939?style=for-the-badge&logo=Jenkins&logoColor=white" /><br>
    </td>
    <td>
      <img src="https://skillicons.dev/icons?i=matlab" />
    </td>
 </tr>
</table>

## IDE/GUI's I like
<p align="center">
  <img src="https://img.shields.io/badge/-positron-61DAFB?style=for-the-badge&logo=visual%20studio%20code&logoColor=white" />
  <img src="https://img.shields.io/badge/Visual_Studio_Code-0078D4?style=for-the-badge&logo=visual%20studio%20code&logoColor=white" />
  <img src="https://img.shields.io/badge/RStudio-75AADB?style=for-the-badge&logo=RStudio&logoColor=white" />
  <img src="https://img.shields.io/badge/Inkscape-000000?style=for-the-badge&logo=Inkscape&logoColor=white" />
</p>

## Blog posts

To list files in a specific folder of a public GitHub repository using R, you can utilize the GitHub API. Here's a concise example:

```{r, echo = FALSE}
posts <- list.files("website/content/blog", 
           "^index.md",
           recursive = TRUE, 
           full.names = TRUE)
posts <- lapply(posts, readLines)

find_key <- function(x, key){
  j <- lapply(x, function(x){
    k <- grep(sprintf("^%s:", key), 
            x, value = TRUE)
    k <- gsub(sprintf("^%s: |'", key), "", k)
    k[1] 
  })
  unlist(j)
}

postdf <- data.frame(
  n = seq_along(posts),
  draft = find_key(posts, "draft") |> 
    grepl(pattern = "true", x = _),
  date = as.Date(find_key(posts, "date")),
  slug = find_key(posts, "slug") |> 
    gsub('\\"', "", x = _),
  title = find_key(posts, "title")
) |> 
  subset(subset = !draft)
postdf$link <-  sprintf("[%s](https://drmowinckels.io/blog/%s)", 
                  postdf$title,
                  postdf$slug)

today    <- Sys.Date()
min_date <- min(postdf$date)
last_post <- as.numeric(max(postdf$date) - today)

postavg <- nrow(postdf)/as.numeric(today - min_date) * 30
postavg <- sprintf("%0.2f", postavg)

postbtw <- as.numeric(today - min_date) / nrow(postdf)
postbtw <- sprintf("%s", round(postbtw, digits = 0))

```


ðŸŽ‰ [DrMowinckels.io](https://drmowinckels.io/) has **`r nrow(postdf)`** posts since **`r min_date`**!

ðŸ“… That's a post roughly every **`r postbtw`** days, or about **`r postavg`** posts per month.

âœï¸ The last post was published **`r abs(last_post)`** days ago (`r tail(postdf, 1)$link`).

ðŸ˜‰ I'll post as often as I am able, and hope people find it interesting. I'd love your feedback in the comments!

```{r 'plot', echo = FALSE,  fig.width=10, fig.height=2.5}
library(lattice)

postdf$ones <- 1

# Assuming postdf is loaded and has a 'date' column
trellis.par.set(background = list(col="transparent"))

xyplot(ones ~ date, 
       data = postdf,
       type = 'p',
       pch = "|",  
       cex = 5,   
       col = "cyan3",
       xlab = "",
       ylab = "",
       main = "Published posts",
       scales = list(x = list(cex = 1.4), y = list(draw = FALSE)),
       strip = FALSE,  # Removes strip labels
       axis.line = list(col = "transparent"),
       layout = c(1, 1),  # Single panel
       par.settings = list(
         strip.border = list(col = "transparent"), #making the border transparent
         axis.line = list(col = "transparent") #making the axes transparent
       )
      )

```

<details><summary>ðŸ“‚ Click to expand a full list of posts</summary>

```{r posts-table, results='asis', echo = FALSE}
data.frame(
  Date = rev(postdf$date),
  Title = rev(postdf$link)
) |> 
  knitr::kable()
```
</details>


## My down time
<p align="center">
  <img src="https://img.shields.io/badge/Amazon%20Prime-00A8E1?style=for-the-badge&logo=netflix&logoColor=white" />
  <img src="https://img.shields.io/badge/Netflix-E50914?style=for-the-badge&logo=netflix&logoColor=white" />
  <img src="https://img.shields.io/badge/Steam-000000?style=for-the-badge&logo=steam&logoColor=white" />
  <img src="https://img.shields.io/badge/Spotify-1ED760?&style=for-the-badge&logo=spotify&logoColor=white" />
  <img src="https://camo.githubusercontent.com/0ff8e3b5f017aed3d006a903cb50b7d7d6fd1fa6bf8e1c020270c6c7c76d0870/68747470733a2f2f696d672e736869656c64732e696f2f7374617469632f76313f7374796c653d666f722d7468652d6261646765266d6573736167653d4170706c652b545626636f6c6f723d303030303030266c6f676f3d4170706c652b5456266c6f676f436f6c6f723d464646464646266c6162656c3d" />
</p>

_Updated `r Sys.time()`_
